Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2023-10-23 manuscript.Rmd
cite höfler

>>>>

We believe that our reasoning is quite similar to @hoflerMeansValuableExploration2022, who call for transparent exploration using preregistration.
We could be surer of our agreement, if they had formulated their arguments within a mathematical framework, which would also have helped to dissolve an apparent conflict in their definitions of confirmation, exploration, and transparency.
On the one hand, they define "The principle difference between confirmation and exploration is that confirmation adheres to an evidential norm for the test of a hypothesis to pass.", but then suggest that transparent exploration can be conducted using inferences tests as a filtering mechanism.
Their distinction between confirmation, intransparent and transparent exploration are otherwise just as well placed along the dimensions, theoretical risk and uncertainty about theoretical risk.
